---
title: "project-3"
author: "Rohini kolli"
date: '2022-05-07'
output:

  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install.packages('stringr')
install.packages('tidytext')
install.packages('janeaustenr')
install.packages('ggplot2')
install.packages('tidyr')
install.packages('igraph')
install.packages('ggraph')
install.packages('tm')
install.packages('plyr')
install.packages('readr')
install.packages('dplyr')
install.packages('stringi')
install.packages('RColorBrewer')
install.packages('tidyverse')
```{r}
library(stringr)
library(tidytext)
library(janeaustenr)
library(ggplot2)
library(tidyr)
library(igraph)
library(ggraph)
library(tm)
library(plyr)
library(readr)
library(dplyr)
library(stringi)
library(RColorBrewer)
library(tidyverse)

```


```{r}
#TASK1
#Importing and preprocessing data
keyword_data<- read.csv("Keyword_data.csv")
keywords = subset(keyword_data, select = -c(Title))
keywords <- data.frame(lapply(keywords, str_to_title))
#2. Creating adjacency matrix
variable <- c()
variable <- as.character(unique(unlist(keywords)))

variable1 <- tolower(stri_remove_empty(variable, na_empty = FALSE))
adj_matrix <- matrix(0,nrow = length(variable1),ncol=length(variable1))
rownames(adj_matrix) <- c(variable1)
colnames(adj_matrix) <- c(variable1)



n_rows <- dim(keywords)[1]
n_cols <- dim(keywords)[2]
# Create a weighted adjacency matrix
keywords1 <- keyword_data[!is.na(keyword_data$`Keyword.1`),]
number <- length(keywords1)

for(x in 1:n_rows){
  for(y in 1:n_cols) {
    for(z in 1:n_cols) {
      key1 <- tolower(keywords[[x, y]])
      key2 <- tolower(keywords[[x, z]])
      if((key1 !="")&&(key2 != "") && (key1 != key2)) {
        adj_matrix[key1,key2] <- adj_matrix[key1,key2] + 1
      }
    }
  }
}
```



```{r}
# 3. Creating a network from the adjaceny matrix
network_graph<-graph_from_adjacency_matrix(adj_matrix,mode="undirected", weighted = TRUE)

plot(network_graph,edge.label=E(network_graph)$weight, 
     vertex.frame.color="red",vertex.label.color="black",
     vertex.size=2,edge.label.color="black")
     

```

```{r}
# 4. Degree of network
Degree <- degree(network_graph, mode="all")
Degree <- data.frame(Degree)
Degree

```

```{r}
# 4. Strength of network
strength <- strength(network_graph, mode="all")
strength <- data.frame(strength)
strength

```


```{r}
#5 top 10 nodes by degree and strength
Top_degree <- Degree %>% arrange(desc(Degree)) %>% slice(1:10)
Top_degree

Top_strength <- strength  %>% arrange(desc(strength)) %>% slice(1:10)
Top_strength

```


```{r}
# 6.top 10 pairs by weight
data.frame(Top_10_node_by_Strength = Top_strength, Top_10_node_by_Degree = Top_degree)

Top_10_pairs_weight <- data.frame()
for (i in 1:248)
  for (j in 1:248)
    if ((i != j) && (i > j)) {
      Top_10_pairs_weight <- rbind(Top_10_pairs_weight, data.frame(N1 = row.names(adj_matrix)[i], N2 = row.names(adj_matrix)[j], Count = adj_matrix[i,j]))
    }

Top_10_pairs_weight %>% 
  arrange(desc(Count)) %>% 
  head(10)
```
```{r}
#7 degree vs average strength
gen_table<- merge(Degree,strength, by=0, all=TRUE)
Avg_Strength <- gen_table %>% 
  group_by(Degree) %>% 
  summarise(Avg_Strength = mean(strength))
plot <- ggplot(Avg_Strength, aes(x=(Degree), y=(Avg_Strength))) + geom_point(color='Steelblue')
plot

```





#TASK2
```{r}
csv.2017 <- read.csv("2017.csv")
csv.2018 <- read.csv("2018.csv")
csv.2019 <- read.csv("2019.csv")
csv.2020 <- read.csv("2020.csv")
csv.2021 <- read.csv("2021.csv")
csv.2022 <- read.csv("2022.csv")

```


```{r}
#assigning all csv in one
twitterfiles <- dir(pattern = "csv.*")
twitterfiles

#combining the csv
mergedfile = ldply(twitterfiles, read_csv)
# converting date column
mergedfile$date <- strptime(mergedfile$date, format='%Y-%m-%d  %H:%M:%S')
# adding year column
mergedfile$year <- format(mergedfile$date,"%Y") 
# filtering by year greater than 2017 and language by English 
mergedfile <- mergedfile %>% 
                filter(language=='en', year %in% c("2017", "2018", "2019", "2020", "2021","2022")) 
                 
mergedfile <- data.frame(year=mergedfile$year, tweet=mergedfile$tweet)
stopwords <- read.table('stopwords-1.txt')

```

```{r}
#### Cleaning Data
mergedfile$tweet <- str_to_lower(mergedfile$tweet) # converting strings to lower case
mergedfile$tweet <- gsub("@\\w+", "", mergedfile$tweet) # removing mentions
mergedfile$tweet <- gsub("[[:digit:]]", "", mergedfile$tweet) # removing numbers
words_df <- mergedfile %>%
            unnest_tokens(word, tweet) %>% # tokennizing words
            filter(!word %in% stopwords$V1, # removing stopwords
                   !word %in% c("https", "t.co", "amp"), # removing urls and links
                   !grepl("^\\d+\\w\\d*", word),
                   !grepl("[^\x01-\x7F]+", word)) %>% 
            count(year, word, sort=T) # computing word count per year
```
#### Computing Word Frequencies
```{r}
total_words <- words_df%>% 
                  group_by(year) %>% 
                  summarize(total_words = sum(n))
words_df <- left_join(words_df, total_words)
words_df$frequency <- words_df$n/words_df$total_words # calculating word frequencies
```
#### Top 10 Words by Year
```{r}
year_df <- data.frame(year=numeric(0), word=character(0), frequency=numeric(0))
for (i in 2017:2022){
  temp_df <- head(subset(words_df, year==i),10)
  temp_df <- temp_df[, !names(temp_df) %in% c('n','total_words')]
  year_df <- rbind(year_df, temp_df)
}
```
##### Year 2017
```{r}
filter(year_df, year==2017)
```
##### Year 2018
```{r}
filter(year_df, year==2018)
```

##### Year 2019
```{r}
filter(year_df, year==2019)
```

##### Year 2020
```{r}
filter(year_df, year==2020)
```


##### Year 2021
```{r}
filter(year_df, year==2021)
```
##### Year 2022
```{r}
filter(year_df, year==2022)
```
#### Plotting Histograms of frequencies per year
##### Year 2017
```{r}
df2017 <- filter(words_df, year==2017)
ggplot(df2017, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=30) +
  xlim(NA, 0.007)
```

##### Year 2018
```{r}
df2018 <- filter(words_df, year==2018)
ggplot(df2018, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=30) +
  xlim(NA, 0.007)
```

##### Year 2019
```{r}
df2019 <- filter(words_df, year==2019)
ggplot(df2019, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=30) +
  xlim(NA, 0.007)
```

##### Year 2020
```{r}
df2020 <- filter(words_df, year==2020)
ggplot(df2020, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=30) +
  xlim(NA, 0.007)
```

##### Year 2021
```{r}
df2021 <- filter(words_df, year==2021)
ggplot(df2021, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=30) +
  xlim(NA, 0.007)
```

##### Year 2022
```{r}
df2022 <- filter(words_df, year==2022)
ggplot(df2022, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=30) +
  xlim(NA, 0.007)
```
#### Zipf’s Law / log-log plots of word frequencies and rank

```{r}
freq_by_rank <- words_df %>% 
  group_by(year) %>% 
  mutate(rank = row_number(), 
         `term frequency` = frequency) %>%
  ungroup()
cols <- brewer.pal(6, "Spectral")
freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = year)) + 
  geom_line(size = 1.1, alpha = 0.8, show.legend = T) + 
  scale_x_log10() +
  scale_y_log10() +
  scale_color_manual(values = cols)
```
```{r}
#### Creating Bigrams
##### Reading DataFrame again
csv.2017 <- read.csv("2017.csv")
csv.2018 <- read.csv("2018.csv")
csv.2019 <- read.csv("2019.csv")
csv.2020 <- read.csv("2020.csv")
csv.2021 <- read.csv("2021.csv")
csv.2022 <- read.csv("2022.csv")

#assigning all csv in one
twitterfiles <- dir(pattern = "csv.*")
twitterfiles

#combining the csv
twitter_bigram_df = ldply(twitterfiles, read_csv)
# converting date column
twitter_bigram_df$date <- strptime(twitter_bigram_df$date, format='%Y-%m-%d  %H:%M:%S')
# adding year column
twitter_bigram_df$year <- format(twitter_bigram_df$date,"%Y") 
# filtering by year greater than 2017 and language by English 
twitter_bigram_df <- twitter_bigram_df %>% 
                filter(language=='en', year %in% c("2017", "2018", "2019", "2020", "2021","2022")) 
tweets_bigram_df <- data.frame(year=twitter_bigram_df$year, tweet=twitter_bigram_df$tweet)

tweets_bigram_df$tweet <- str_to_lower(tweets_bigram_df$tweet) # converting strings to lower case
tweets_bigram_df$tweet <- gsub("@\\w+", "", tweets_bigram_df$tweet) # removing mentions
tweets_bigram_df$tweet <- gsub("[[:digit:]]", "", tweets_bigram_df$tweet) # removing numbers
```



##### Creating Bigrams DataFrame
```{r}
bigrams_df <- tweets_bigram_df %>%
            unnest_tokens(bigram, tweet, token = "ngrams", n = 2) 
```

##### Cleaning the data
```{r}
bigrams_df <- bigrams_df %>%
  separate(bigram, c("word1", "word2"), sep = " ")
bigrams_df <- bigrams_df %>%
                filter( !word1 %in% c("https", "t.co", "amp"), 
                        !word2 %in% c("https", "t.co", "amp"),
                        !grepl("^\\d+\\w\\d*", word1),
                        !grepl("[^\x01-\x7F]+", word1),
                        !grepl("^\\d+\\w\\d*", word2),
                        !grepl("[^\x01-\x7F]+", word2))
bigrams_df <- bigrams_df %>%
                filter(!word1 %in% stopwords$V1) %>%
                filter(!word2 %in% stopwords$V1)
```
##### Counting Bigrams
```{r}
bigrams_df <- bigrams_df %>% 
                count(year, word1, word2, sort = T)
bigrams_df <- bigrams_df[complete.cases(bigrams_df),]
```

##### Year 2017
```{r}
df2017 <- filter(bigrams_df, year==2017)
df2017 <- df2017[,2:4]
bigram_graph <- df2017 %>%
  filter(n > 6) %>% # filtering pairs with frequency less than 3
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.05, "inches"))
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```

##### Year 2018
```{r}
df2018 <- filter(bigrams_df, year==2018)
df2018 <- df2018[,2:4]
bigram_graph <- df2018 %>%
  filter(n > 9) %>% # filtering pairs with frequency less than 4
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.05, "inches"))
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
##### Year 2019
```{r}
df2019 <- filter(bigrams_df, year==2019)
df2019 <- df2019[,2:4]
bigram_graph <- df2019 %>%
  filter(n > 4) %>%  # filtering pairs with frequency less than 4
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.05, "inches"))
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
##### Year 2020
```{r}
df2020 <- filter(bigrams_df, year==2020)
df2020 <- df2020[,2:4]
bigram_graph <- df2020 %>%
  filter(n > 5) %>%  # filtering pairs with frequency less than 4
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.05, "inches"))
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
##### Year 2021
```{r}
df2021 <- filter(bigrams_df, year==2021)
df2021 <- df2021[,2:4]
bigram_graph <- df2021 %>%
  filter(n > 4) %>%  # filtering pairs with frequency less than 1
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.05, "inches"))
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
##### Year 2022
```{r}
df2022 <- filter(bigrams_df, year==2022)
df2022 <- df2022[,2:4]
bigram_graph <- df2022 %>%
  filter(n > 2) %>%  # filtering pairs with frequency less than 1
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.05, "inches"))
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```